---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GLFishStockR

<!-- badges: start -->
<!-- badges: end -->

The package provides a number of low level functions that fetch data
from the Great Lakes fish stocking database for further analayis
and reporting in R.


## Example

GLFishStocker provides a number of functions that can be use to fetch
data from the Great Lakes Fish Stocking Database API (www.fsis.glfc.org)

The functions in GLFishSocker expose methods that allow us to easily
get data into R, including the lakes, contributing agencies, and
associated management/spatial units.

```{r example}
library(GLFishStockR)
## basic example code

get_lakes()
agencies <- get_agencies()
head(agencies)

mus <- get_management_units()
head(mus)

filters <- list(
  "lake" = "MI"
)
mus <- get_management_units(filters)
head(mus)

jurisdictions <- get_jurisdictions()
head(jurisdictions)


filters <- list(
  "lake" = "MI"
)
jurisdictions <- get_jurisdictions(filters)
head(jurisdictions)


get_state_provinces()
get_state_provinces(list("country" = "USA"))
head(get_grid10s(filters))
```

We can get all of the species, strains and raw (detailed) strains too:

```{r species_and_strains}

species <- get_species()
head(species)

strains <- get_strains()
head(strains)

raw_strains <- get_raw_strains()
head(raw_strains)
```
We can fetch all of the values used for lifestages, marks, and yearling equivalent factors:

```{r stocking_methods_and_lifestages}

lifestages <- get_lifestages()
head(lifestages)

marks <- get_marks()
head(marks)

yreq <- get_yreq_factors()
head(yreq)

# we can get them for a single species or lifestage too
get_yreq_factors(list(species = "LAT"))
```

We can get stocking events based on a large number of attributes
including (but not limited to lake, species, strain, agency,
lifestage, stocking method, jursidiction, managment unit, or year.

```{r stocking_events]}

filters <- list(
  "lake" = "HU",
  "species" = c("RBT", "LAT", "BNT"),
  "first_year" = 2012
)
events <- get_stocking_events(filters)

nrow(events)
head(events)
```

We can also find stocking events that were associatd with specific coded
wire tags, tag attriutes, or attributes of the stocked fish or stocking
event.

```{r cwts_events]}
filters <- list(
  cwt_number = "630157"
)

cwt_events <- get_cwt_events(filters)
head(cwt_events)
```
